---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Jeremy



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
cces$Ideology <- cces$ideo5 %>% recode(`1`="Very Liberal",`2`="Liberal",`3`="Moderate",`4`="Conservative",`5`="Very Conservative")

cces %>% ggplot(aes(x=Ideology,fill=Ideology)) + geom_bar() + labs(title="Respondent Ideology",y="Count") + guides(fill="none")

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
cces$Ideology <- cces$ideo5 %>% recode(`1`="Very Liberal",`2`="Liberal",`3`="Moderate",`4`="Conservative",`5`="Very Conservative")
cces$rec_religimp <- cces$pew_religimp %>% recode(`1`="Very imp.",`2`="Somewhat imp.",`3`="Not too imp.",`4`="Not imp.")

cces %>% ggplot(aes(x=rec_religimp,fill=Ideology)) + geom_bar() + labs(x="Importance of Religion",y="Count",title="Importance of Religion by Ideology")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
Students <- c("Amanda","Betty","Carol")
Semesters <- c(1:6)
toydat <- expand.grid(Student=Students, Semester=Semesters)
toydat$Grade <- runif(18,80,100)

toydat %>% ggplot(aes(x=Semester,y=Grade,color=Student)) + geom_line(show.legend=FALSE) + labs(title="Student Grades by Semester") + facet_wrap(~Student)
```
